\plaintitle

### 2017-04-25 statistical-quorum.tex
More on introduction.

There have been many improvements proposed to this basic form and various analysis made.
\todo{Add references.}
In this paper we focus on the question of \emph{quorum} and how high the quorum should be.
Quorum is the minimum number of members participating in voting for voting to be seen as representative of the whole
community, i.e., legitimate.
If quorum is too low, decisions adopted might not represent the community.
If it is too high, the community might have issues achieving the quorum.
Not enough members might decide to participate in voting, or members might on purpose boycott voting to
prevent decision to be adopted, even if those opposing it are in minority.
Communities often decide quorum arbitrary\footnote{Robert's Rules of Order states that the quorum
``should approximate the largest number that can be depended on to attend any meeting except in very bad weather
or other extremely unfavorable conditions.''~\cite{roberts}}
and try to increase participation of members in communities' democratic processes.
\todo{Add references.}
Moreover, many democratic communities have issues achieving quorum which hinders their operation.
\todo{Add references.}

>>>>

There have been many improvements proposed to this basic form and various analysis made.
\todo{Add references.}
In this paper we focus on the question of \emph{quorum} and how high the quorum should be.
Quorum is the minimum number of members participating in voting for voting to be seen as representative of the whole
community, i.e., legitimate.
If quorum is too low, decisions adopted might not represent the community.
If it is too high, the community might have issues achieving the quorum.
Not enough members might decide to participate in voting, or members might on purpose boycott voting to
prevent decision to be adopted, even if those opposing it are in minority.
Communities often decide quorum arbitrary\footnote{Robert's Rules of Order states that the quorum
``should approximate the largest number that can be depended on to attend any meeting except in very bad weather
or other extremely unfavorable conditions.''~\cite{roberts}}
and try to increase participation of members in communities' democratic processes through various means
to address the issue of too low turnout.
\todo{Add references. Mention forced participation in some countries.}
Moreover, many democratic communities have issues achieving quorum which hinders their operation.
\todo{Add references.}

\todo[inline]{Structure of the rest of the paper.}

\section{Related Work}
